\documentclass{article}
\usepackage{graphicx}
\author{Noah FitzPatrick}
\title{Aproximating the Distance Between Earth and Mars Over Time}
\date{April 1st, 2021}
\begin{document}
\maketitle
%\section{Abstract and Intro}
\input{AbsandIntr}
\section{Procedures}
\input{Procedures}
%\section{Data}
\input{Data}
\section{Conclusion}
If the only issue with this method of approximation is the width of the $\Delta\theta$ interval, than it should work
fine with a more powerful computer. If, however, it is a more fundamental issue with the method which was somehow 
overlooked, more work will need to be done. Based on this project alone, it at least seems that Kepler's laws were 
effectivley formatted into equations of velocity capable of being computed quickly and accurately. Formulas that
could integrate the velocity equation directly could be used to better analyze the error of this method. 
%\section{Bibliography}
\begin{thebibliography}{}
	\bibitem[Taylor, 2005]{taylor} Taylor, John r., Classical Mechanics. University Science Books, 2005, pg. 93, 
		309-315.
	\bibitem[Kepler's Laws, 2016]{georgia1} Hyper Physics. Kepler's Laws. Georgia State University, 2016,http://hyperphysics.phy-astr.gsu.edu/hbase/hph.html. Accessed 31 March, 2021.
%	\bibitem[Developing Kepler's Law of Orbits, 2016]{georgia2} Hyper Physics. Developing Kepler's Law of Orbits. Georgia State University, 2016, http://hyperphysics.phy-astr.gsu.edu/hbase/Mechanics/keplerd.html#c2. Accessed 31 March, 2021.
        \bibitem[INOVA, 2010]{scope} INOVA. Solar System Scope. INOVA, 2010, https://www.solarsystemscope.com/. Accessed 31 March, 2021.

\end{thebibliography}
\end{document}
%@book{taylor, 
%	title = {Classical Mechanics},  
%	author = {John r. Taylor}, 
%	year = {2005}, 
%	publisher = {University Science Books}, 
%	pages = {93, 309-315}
%}

%@online{georgia, 
%	author = {Hyper Physics}, 
%	title = {Kepler's Laws}, 
%	year = {2016},
%	url = {http://hyperphysics.phy-astr.gsu.edu/hbase/hph.html}, 
%	urldate = {2021-04-01}
%}

%@online{georgia2, 
%	author = {Hyper Physics}, 
%	title = {Developing Kepler's Law of Orbits}, 
%	year = {2016}, 
%	publisher = {Georgia State University}, 
%	url = {http://hyperphysics.phy-astr.gsu.edu/hbase/Mechanics/keplerd.html#c2}, 
%	urldate = {2021-04-01}
%}

%@online{scope, 
%	title = {Solar System Scope}, 
%	year = {2010}, 
%	url = {https://www.solarsystemscope.com/},
%	publisher = {INOVE}, 
%	urldate = {2021-04-01}
%}
